The \dealii{} Library, Version 9.3

### 2021-06-24 9.3/paper.tex
FEIV example

>>>>

\newcommand{\jump}[1]{\left[\!\left[ #1 \right]\!\right]}
\newcommand{\average}[1]{\left\{\!\left\{ #1 \right\}\!\right\}}
For example, the interface terms of the SIPG formulation for a Laplace problem 
\[
\sum_{F} -
    \left< \jump{v_h}, \average{ \nabla u_h} \cdot  \mathbf n \right>_F
   -\left<\average{ \nabla v_h }\cdot \mathbf n,\jump{u_h}\right>_F
   +\left<\jump{v_h}, \sigma \jump{u_h} \right>_F
\]
with face jump $\jump{\cdot}$ and average $\average{\cdot}$
can be implemented as (also see \texttt{step-74}):
\begin{c++}
  cell_matrix(i, j) +=
  (- fe_iv.jump(i, q) * (fe_iv.average_gradient(j, q) * n)
   - (fe_iv.average_gradient(i, q) * n) * fe_iv.jump(j, q)
   + penalty * fe_iv.jump(i, q) * fe_iv.jump(j, q)  
  ) * JxW[q];
\end{c++}
